---
title: "p8105_hw6_wz2590"
author: "Weiheng Zhang"
date: "2021/11/24"
output: github_document
---

```{r message = FALSE}
library(tidyverse)
library(dplyr)
library(patchwork)
library(modelr)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r}
birthweight_clean = 
  readr::read_csv("data/birthweight.csv") %>%
  mutate(
    babysex = factor(babysex, labels = c("Male", "Female")),
    frace = factor(frace, levels = c(1, 2, 3, 4, 8, 9), labels = c("White", "Black", "Asian"," Puerto Rican", "Other", "Unknown")),
    malform = factor(malform, labels = c("Absent", "Present")),
    mrace = factor(mrace,  c(1, 2, 3, 4, 8, 9), labels = c("White", "Black", "Asian"," Puerto Rican", "Other", "Unknown"))
    ) %>% 
  janitor::clean_names()

birthweight_clean

birthweight_clean %>% 
  select(everything()) %>% 
  summarize_all(funs(sum(is.na(.))))
```
There is no NA in this dataset. We can move on to the next step. 

After some literature search, I will use scatter plots to browse some potential variables that may be correlated to the birth weight.
```{r}
birthweight_clean %>% 
  ggplot(aes(x = bhead, y = bwt)) + geom_point()

birthweight_clean %>% 
  ggplot(aes(x = blength, y = bwt)) + geom_point()

birthweight_clean %>% 
  ggplot(aes(x = gaweeks, y = bwt)) + geom_point()

birthweight_clean %>% 
  ggplot(aes(x = delwt, y = bwt)) + geom_point()

birthweight_clean %>% 
  ggplot(aes(x = fincome, y = bwt)) + geom_point()

birthweight_clean %>% 
  ggplot(aes(x = smoken, y = bwt)) + geom_point()

```



According to the trends shown in the scatter plots, I will choose. I will choose the variables "baby’s head circumference at birth", "baby’s length at birth", "gestational age in weeks", and "mother's weight at delivery".
```{r}
proposed =
  lm(bwt ~ bhead + blength + gaweeks + delwt, data = birthweight_clean) 
broom::tidy(proposed) %>% 
    knitr::kable()
```


Now I will build a plot of model residuals against fitted values.

```{r}
birthweight_clean %>%
  add_residuals(proposed) %>%
  add_predictions(proposed) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()  + 
  labs(title = "Plot of Model Residuals Against Fitted Values", 
       x = "Fitted", 
       y = "Residuals")
```


Other two models to compare with.
Model 1: Using length at birth and gestational age as predictors (main effects only)
Model 2: sing head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_clean)

model2 = lm(bwt ~bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex , data = birthweight_clean)

broom::tidy(model1) %>% 
    knitr::kable()

broom::tidy(model2) %>% 
    knitr::kable()
```

```{r}
birthweight_clean %>%
  add_residuals(model1) %>%
  add_predictions(model1) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()  + 
  labs(title = "Model1: Residuals Against Fitted Values", 
       x = "Fitted", 
       y = "Residuals")

birthweight_clean %>%
  add_residuals(model2) %>%
  add_predictions(model2) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()  + 
  labs(title = "Model2: Residuals Against Fitted Values", 
       x = "Fitted", 
       y = "Residuals")
```


Perform cross validation.
```{r}
birthweight_CV =
  crossv_mc(birthweight_clean, 100) %>% 
  mutate(train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(proposed = map(train, ~proposed, data = .x),
           model1 = map(train, ~model1, data = .x),
           model2 = map(train, ~model2, data = .x)) %>% 
    mutate(rmse_proposed = map2_dbl(proposed, test, ~rmse(model = .x, data = .y)),
           rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data =.y)),
           rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)))
```


```{r}
birthweight_CV %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(
      title = "Cross Validation of Specified Models",
      x = "Model",
      y = "Root Mean Squared Error")
```

After cross-validation, I find out that my proposed model, which is the model that used "baby’s head circumference at birth", "baby’s length at birth", "gestational age in weeks" and "mother's weight at delivery", has the smallest RMSE and thus has the best fitting.









